From Freebase to Wikidata: The Great Migration

### 2015-10-16 paper.tex
fix year for Freebase to Wikidata decision
The decision was announced in 2014. This is also mentioned later in the paper.
open source -> open source software
Something is released either under an open source license or as open source software

\begin{abstract}
Collaborative knowledge bases that make their data freely available in a~machine-readable form
are central for the data strategy of many projects and organizations.
The two major collaborative knowledge bases are Google's Freebase and Wikimedia's Wikidata.
Due to the success of Wikidata, Google decided in 2015 to offer the content of Freebase
to the Wikidata community.
In this paper, we describe the ongoing transfer efforts and data mapping challenges,
and provide an analysis of the effort so far.
We describe the \emph{Primary Sources Tool}, which aims to facilitate
this and future data migrations.
Throughout the migration, we have gained insights into both Wikidata and Freebase,
and share and discuss detailed statistics on both knowledge bases. 
\end{abstract}

@@

In this paper we describe how we support the Wikidata community with
the migration of Freebase content to Wikidata.
We created the \emph{Primary Sources Tool},
released as open source to facilitate the transfer of the Freebase dataset.
The \emph{Primary Sources Tool} is also developed with an eye on
future data migrations from other source.
We created and published mappings of the Freebase dataset.
Throughout the migration, we have gained insights into both Wikidata and Freebase,
and share and discuss detailed statistics on both knowledge bases.

>>>>

\begin{abstract}
Collaborative knowledge bases that make their data freely available in a~machine-readable form
are central for the data strategy of many projects and organizations.
The two major collaborative knowledge bases are Google's Freebase and Wikimedia's Wikidata.
Due to the success of Wikidata, Google decided in 2014 to offer the content of Freebase
to the Wikidata community.
In this paper, we describe the ongoing transfer efforts and data mapping challenges,
and provide an analysis of the effort so far.
We describe the \emph{Primary Sources Tool}, which aims to facilitate
this and future data migrations.
Throughout the migration, we have gained insights into both Wikidata and Freebase,
and share and discuss detailed statistics on both knowledge bases. 
\end{abstract}

@@

In this paper we describe how we support the Wikidata community with
the migration of Freebase content to Wikidata.
We created the \emph{Primary Sources Tool},
released as open source software to facilitate the transfer of the Freebase dataset.
The \emph{Primary Sources Tool} is also developed with an eye on
future data migrations from other source.
We created and published mappings of the Freebase dataset.
Throughout the migration, we have gained insights into both Wikidata and Freebase,
and share and discuss detailed statistics on both knowledge bases.
